Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
parse scales, edits social scale

## Varying scale in multilayer networks
### Social scale

We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 - 500 m. For example, at the finest social
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest social scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->

>>>>

## Varying scale in multilayer networks
<!--

social scale: variable is spatial distance threshold
spatial scale: variable is land cover resolution
temporal scale: variable is temporal window
temporal scale: variable is number of observations
-->

### Social scale

We modified the spatial distance threshold used for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 and 500 m (5, 25, 50, 75, 100, 250, 500). For example, at the finest
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->
